MG7: Configurable and scalable 16S metagenomics data analysis -- new methods optimized for massive cloud computing

### 2015-09-12 docs/paper/out/paper.tex
remove duplicate numbering in sections -- paper

\section{1. Introduction}\label{introduction}

@@

\section{2. Materials and Methods}\label{materials-and-methods}

\subsection{2.x Amazon Web Services}\label{x-amazon-web-services}

\subsection{2.x Scala}\label{x-scala}

@@

\subsection{2.x Statika}\label{x-statika}

@@

\subsection{2.x Datasets}\label{x-datasets}

@@

\subsection{2.x Loquat}\label{x-loquat}

@@

\subsection{2.x Type-safe DSLs for BLAST and
FLASH}\label{x-type-safe-dsls-for-blast-and-flash}

@@

\subsubsection{2.x.a BLAST DSL}\label{x.a-blast-dsl}

@@

\subsubsection{2.x.b FLASH DSL}\label{x.b-flash-dsl}

@@

\subsection{2.x Bio4j}\label{x-bio4j}

@@

\section{3. Results}\label{results}

\subsection{3.1 Overview}\label{overview}

@@

\subsection{3.x 16S Reference Database
Construction}\label{x-16s-reference-database-construction}

@@

\subsection{3.x Bio4j and Graph
Databases}\label{x-bio4j-and-graph-databases}

\subsection{3.x MG7 Pipeline
Description}\label{x-mg7-pipeline-description}

\subsection{3.x Taxonomic Assignment
Algorithms}\label{x-taxonomic-assignment-algorithms}

\subsubsection{3.x.y Lowest Common Ancestor based Taxonomic
Assignment}\label{x.y-lowest-common-ancestor-based-taxonomic-assignment}

@@

\subsubsection{3.x.z Best BLAST hit taxonomic
assignment}\label{x.z-best-blast-hit-taxonomic-assignment}

@@

\subsection{3.x Other}\label{x-other}

@@

\subsection{3.x Using MG7 with some example
data-sets}\label{x-using-mg7-with-some-example-data-sets}

@@

\subsection{3.7 MG7 availability}\label{mg7-availability}

@@

\section{4. Discussion}\label{discussion}

\subsection{4.1 Novelty points of MG7}\label{novelty-points-of-mg7}

@@

\subsection{4.2 Designed for future
challenges}\label{designed-for-future-challenges}

@@

\subsection{4.3 MG7 Future developments}\label{mg7-future-developments}

\subsubsection{4.3.1 Comparison of groups of
samples}\label{comparison-of-groups-of-samples}

\subsubsection{4.3.2 Interactive visualizations using the output files
of MG7 (Biographika
project)}\label{interactive-visualizations-using-the-output-files-of-mg7-biographika-project}

\section{5 Acknowledgements}\label{acknowledgements}

@@

\section{6 References}\label{references}

>>>>

\section{Introduction}\label{introduction}

@@

\section{Materials and Methods}\label{materials-and-methods}

\subsection{Amazon Web Services}\label{amazon-web-services}

\subsection{Scala}\label{scala}

@@

\subsection{Statika}\label{statika}

@@

\subsection{Datasets}\label{datasets}

@@

\subsection{Loquat}\label{loquat}

@@

\subsection{Type-safe DSLs for BLAST and
FLASH}\label{type-safe-dsls-for-blast-and-flash}

@@

\subsubsection{BLAST DSL}\label{blast-dsl}

@@

\subsubsection{FLASH DSL}\label{flash-dsl}

@@

\subsection{Bio4j}\label{bio4j}

@@

\section{Results}\label{results}

\subsection{Overview}\label{overview}

@@

\subsection{16S Reference Database
Construction}\label{s-reference-database-construction}

@@

\subsection{Bio4j and Graph Databases}\label{bio4j-and-graph-databases}

\subsection{MG7 Pipeline Description}\label{mg7-pipeline-description}

\subsection{Taxonomic Assignment
Algorithms}\label{taxonomic-assignment-algorithms}

\subsubsection{Lowest Common Ancestor based Taxonomic
Assignment}\label{lowest-common-ancestor-based-taxonomic-assignment}

@@

\subsubsection{Best BLAST hit taxonomic
assignment}\label{best-blast-hit-taxonomic-assignment}

@@

\subsection{Other}\label{other}

@@

\subsection{Using MG7 with some example
data-sets}\label{using-mg7-with-some-example-data-sets}

@@

\subsection{MG7 availability}\label{mg7-availability}

@@

\section{Discussion}\label{discussion}

\subsection{Novelty points of MG7}\label{novelty-points-of-mg7}

@@

\subsection{Designed for future
challenges}\label{designed-for-future-challenges}

@@

\subsection{MG7 Future developments}\label{mg7-future-developments}

\subsubsection{Comparison of groups of
samples}\label{comparison-of-groups-of-samples}

\subsubsection{Interactive visualizations using the output files of MG7
(Biographika
project)}\label{interactive-visualizations-using-the-output-files-of-mg7-biographika-project}

\section{Acknowledgements}\label{acknowledgements}

@@
